Applying Gaussian Process Regression to Predict Changes in Stock Price

### 2014-05-10 paper/paper.tex
Paper author changes

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amssymb}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09

@@

\author{
Stephanie deWet \\
Department of Computer Sciences\\
University of Wisconsin - Madison \\
Madison, WI 53705 \\
\texttt{sdewet@cs.wisc.edu} \\
\And
Saswati De \\
Department of Computer Sciences\\
University of Wisconsin - Madison \\
Madison, WI 53705 \\
\texttt{sde@cs.wisc.edu} \\
}

@@

\begin{abstract}
\end{abstract}

@@

\section{Initial Data Processing}
Our data set consists of information collected on a single stock, including instantaneous stock prices and instantaneous values of 27 parameters ($P$) known to have some affect on the price.
These values are taken at many different time stamps.
Our goal is to predict the stock price in the near future, given current values of the parameters.

@@

\subsubsection*{Acknowledgments}
Thanks to Jerry Zhu for an excellent class, and to Rasmussen and Willams for their excellent book.

\subsubsection*{References}
\small{
}

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
%\usepackage{babel}

%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09

\author{
Stephanie deWet \\
Department of Computer Sciences\\
University of Wisconsin - Madison \\
Madison, WI 53705 \\
\texttt{sdewet@cs.wisc.edu} \\
\and
Saswati De \\
Department of Computer Sciences\\
University of Wisconsin - Madison \\
Madison, WI 53705 \\
\texttt{sde@cs.wisc.edu} \\
}

@@

@@

\begin{abstract}
Predicting stock prices is an interesting problem for machine learning researchers. In this paper we use Gaussian Processes to model the timeseries representing the change in price of a single stock. Our implementation of the GP model performed well in comparison to other regression models like Linear Regression and PCA Regression.
\end{abstract}

@@

\section{Initial Data Processing}
Our data set (obtained from http://www.tworoads.co.in/trading-competition) consists of information collected on a single stock, including instantaneous stock prices and instantaneous values of 27 parameters ($P$) known to have some affect on the price.
These values are taken at many different time stamps.
Our goal is to predict the stock price in the near future, given current values of the parameters.

@@

\subsubsection*{Acknowledgments}
Thanks to Prof. Zhu for an excellent class.

\subsubsection*{References}
\small{
C.E. Rasmussen \& C.K.I. Williams, Gaussian Processes for Machine Learning. \\
David Mackay, Introduction to Gaussian Processes.\\
Long-term Stock Market Forecasting using Gaussian Processes, Nando de Freitas.
Dataset - http://www.tworoads.co.in/trading-competition}
